### 2021-03-04 papers/jin-thesis/Chapters/4Results.tex
A lot of thesis progress !
Thesis work

\section{Optimized Parameters}
The set of parameters that best fit Yildiz's data are shown in the table below

@@

\section{Stepping Patterns}
The plots that were used to compare with experiment and optimize our parameters are shown below
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{/mc_plots/u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\includegraphics[width=0.6\textwidth]{/mc_plots/u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle. Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement. \textit{Bottom:} One dimensional probability density of step length. Step length defined as final displacement minus the initial displacement. Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.} 
	\label{fig:DataStep}
\end{figure}
The first plot in Figure (\ref{fig:DataStep}) displayed the joint probability density of having a specific final displacement and initial displacement. The linear regression from experiment indicated the functionality between the two with an average final displacement of 9.1nm, indicated from the y-intercept. The second plot in Figure (\ref{fig:DataStep}) displayed the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement. The limitation of experiment was made very obvious here due to their inability to record short step lengths. This factor heavily influenced the parameter fitting because in order to best fit the linear correlation within steps, the model dynein had to take very fast and short steps. Since Yildiz observed a linear regression that averaged 0nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding. The step lengths close to 0nm from Experiment Fig 3A in Figure (\ref{fig:DataStep}) were large step lengths in the off-axis.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/prob_lagging_vs_init_L_-0.5}
	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
	\label{fig:ProbTrail}
\end{figure}

>>>>

\section{Optimized Parameters}\label{sec:Params}
The set of parameters that best fit Yildiz's data are shown in Table (\ref{tab:params}) below.

@@

\section{Stepping Patterns}
The plots that were used to compare with experiment and optimize our parameters are shown below
\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{/mc_plots/thesis_u_final_disp_probability_distribution_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\includegraphics[width=0.6\textwidth]{/mc_plots/thesis_u_step_length_1d_probability_density_30.0_5.50e+09_1.00e+08_0.0_1.0_1.0_120.0_197.0_242.0_-0.5}
	\caption[Final Displacement Probability Distribution]{\textbf{Stepping Probability Distribution Plots.} \textit{Top:} Two dimensional heatmap of binding domain displacement before and after a stepping cycle. Linear regression of the probability distribution indicates a dependence between the final displacement of the step and its initial displacement. \textit{Bottom:} One dimensional probability density of step length. Step length defined as final displacement minus the initial displacement. Model compared to two experimental figures of stepping patterns from \citep{Dewitt2012}.} 
	\label{fig:DataStep}
\end{figure}
The first plot in Figure (\ref{fig:DataStep}) displayed the joint probability density of having a specific final displacement and initial displacement. The linear regression from experiment indicated the functionality between the two with an average final displacement of 9.1nm, indicated from the y-intercept. The second plot in Figure (\ref{fig:DataStep}) displayed the one-dimensional probability density of step lengths, defined as final displacement minus the initial displacement. The limitation of experiment was made very obvious here due to their inability to record short step lengths. This factor heavily influenced the parameter fitting because in order to best fit the linear correlation within steps, the model dynein had to take very fast and short steps. Since Yildiz observed a linear regression that averaged 0nm step lengths without being able to record 0nm, the model dynein was forced to take steps with very quick rebinding. The step lengths close to 0nm from Experiment Fig 3A in Figure (\ref{fig:DataStep}) were large step lengths in the off-axis.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\columnwidth]{../../plots/mc_plots/thesis_prob_lagging_vs_init_L_-0.5}
	\caption[Probability of Lagging Step]{\textbf{Probability of Lagging Step}}
	\label{fig:ProbTrail}
\end{figure}
